Compositional equivalences based on Open pNets

### 2021-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
annex review

For all predicate $\Pred$ for all partial function $\Post$,if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
		 \begin{mathpar}
    \openrule
         {
           \set{\beta}, \Pred\,',\Post\,'}
          {t \OTarrow {\alpha} t'}\in\mathcal{T}
\implies
    \openrule
         {
           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortodot\Post\,'}
         {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
 \in\mathcal{T}
\end{mathpar}
\end{definition}

@@

\end{mathpar}
 there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$
 and  
\begin{multline*}
 \Pred_{s,t} \land \Pred_{OT}\implies\\
%\hspace{1cm}
 \displaystyle{\bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}
\end{multline*}
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.
%\bigskip
%
% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
%and\\
%%\hspace{1cm}
% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x \land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
%     %     \right)$.

@@

We start with a decomposition property: from one open transition of $P[Q]_{j_0}$, we exhibit 
corresponding behaviours of $P$ and $Q$, and determine the relation between their 
predicates.
\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
	Let $\Leaves(Q)=p_l^{l\in L_Q}$ and suppose:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\beta_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$Q$.
\end{lemma}

@@

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~~and~~}
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have:\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}

@@

       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
       	\mathcal{R}$;
       	and  
\begin{multline*}
       	\Pred_{s,p} \land \Pred_{OT}\\
 \implies \bigvee_{x\in X}
       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)
\end{multline*}

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\beta_{j p x y}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  
\begin{multline*}
\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
       	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}
\end{multline*}

@@

       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
       	original predicate relating $s$ and $u$ by definition of the transitive 
       	closure):\\
       	\begin{small}
       		$\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
       		\land \alpha\!=\!\alpha_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)}$.
       	\end{small}

\medskip
\noindent From (*) and (**) we have:\\ 
for all $p$,
       	\begin{small}
       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
       		(\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
       		\land \big( 
       		\Pred_{OT_{pxy}}
       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\big)
       		$

@@

      	\begin{small}     	
$\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{p\in P} (
	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
{~}\hspace{1cm}~ \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
\land \Pred_{OT_{pxy}}\\
~\hspace*{3em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
\\
{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
\land \alpha\!=\!\alpha_{pxy} \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$
  \end{small}

@@

 Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
 $\Leaves(P)=p_l^{l\in L_P}$.
 Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
 $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
 We will consider the relation
%\footnote{$\uplus$ is defined on sets as the disjoint union 
% of the contained indexed 
% sets} 
$\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
 t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
   where $\mathcal{S}_P$ is the set of states of the open automaton of $P$.	We will prove 
 that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
 states: $(\ostate{s_{i}^{i \in L_P\uplus L}},\ostate{{t}_{i}^{i \in L'}\uplus 
 	{s}_{i}^{i \in L_P}}|\Pred_{s,t})\in\mathcal{R}'$. %Those are states of the open 
 %	automata of 
 %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
 Consider an 
 open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
 %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
 %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
 \\[-2ex]     
 \[P[Q]_{j_0}\models\openrule
 {
 	\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
 { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
 			L_P\uplus 
 			L}}}\]
 Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
 Lemma~\ref{lem-decompose} we have:\\[-2ex]
 	\begin{mathpar}
 P\models{\openrule
 	{
 		\beta_j^{j\in J'}, 
 		\Pred\,',  
 		\Post\,'}
 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {\alpha}
 		\ostate{s_{i}'^{\,i\in L_P}}}
 }\\
 Q\models{\openrule
 	{
 		\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 		\Post\,''}
 	{\ostate{s_{i}^{i\in L}} \OTarrow {\alpha_Q}
 		\ostate{s_{i}'^{\,i\in L}}}
 }\end{mathpar}
 and  $\Pred_{OT}\iff \Pred\,'
 \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
 \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
 		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
 $OT'_x$ 
 of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
 \begin{mathpar}
 Q'\models\openrule
 {
 	\beta_{j x}^{j\in J\cap\Holes(Q)}, 
 	\Pred_{OT_x},\Post_{OT_x}}
 {\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
 \end{mathpar}
 and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
 		L'}}|\Pred_{s x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred\,''
 \implies$\\ $\displaystyle{\bigvee_{x\in X}
 \left( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
 \Pred_{OT_x}
 \land \alpha_Q\!=\!\alpha_x \land  
 \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$

@@

 \noindent                        
 \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
 \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
 	%reversed 
 	%substitution 
 	\implies  \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 	\Pred_{OT_x}
 	\land \alpha_Q\!=\!\alpha_x \land  
 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
 }
 \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
 	\implies
 	 \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 		\Pred\,'\land \Pred_{OT_x}
 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
 	 $\end{small}

>>>>

For all predicate $\Pred$ for all partial function $\Post$,if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
		 \begin{mathpar}
    \openrule
         {
           \set{\beta}, \Pred\,',\Post\,'}
          {t \OTarrow {\alpha} t'}\in\mathcal{T}
\quad\implies\quad
    \openrule
         {
           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortodot\Post\,'}
         {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
 \in\mathcal{T}
\end{mathpar}
\end{definition}

@@

\end{mathpar}
 there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
    \openrule
         {
           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTarrow {\alpha_x} t_x}
%         \right)
\end{mathpar}
 such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
 \mathcal{R}$
 and  
\begin{multline*}
 \Pred_{s,t} \land \Pred_{OT}\implies\\
%\hspace{1cm}
 \displaystyle{\bigvee_{x\in X}
   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}
\end{multline*}
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.
%\bigskip
%
% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
%and\\
%%\hspace{1cm}
% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x \land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
%     %     \right)$.

@@

We start with a decomposition property: from one open transition of $P[Q]_{j_0}$, we exhibit 
corresponding behaviours of $P$ and $Q$, and determine the relation between their 
predicates.
\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
	Let $\Leaves(Q)=p_l^{l\in L_Q}$ and suppose:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\beta_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~\qquad\qquad~}
		%\[
		Q\models{\openrule
			{
				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
				\Post\,''}
			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
				\ostate{s_i'^{\,i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred \iff \Pred\,'
		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
		$Q$.
\end{lemma}

@@

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-1ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\quad\text{~~and~~}\quad
%\[
Q\models{\openrule
	{
		\beta_j^{j\in J_Q},
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have:\\[-1ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}

@@

       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
       	\mathcal{R}$;
       	and  
\begin{multline*}
       	\Pred_{s,p} \land \Pred_{OT}\\
 \implies \bigvee_{x\in X}
       	\Big( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)
\end{multline*}

@@

       	\begin{mathpar}  	
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\beta_{j p x y}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  
\begin{multline*}
\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
       	\Big( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
       	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\Big)}
\end{multline*}

@@

       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
       	original predicate relating $s$ and $u$ by definition of the transitive 
       	closure):\\
       	\begin{small}
       		$\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\Big( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
       		\land \alpha\!=\!\alpha_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\Big)}$.
       	\end{small}

\medskip
\noindent From (*) and (**) we have:\\ 
for all $p$,
       	\begin{small}
       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
       		\Big( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\land\Pred_{p,u}}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\Big( \forall j. \beta_j=\beta_{jpx}  \land 
       		(\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\Big( \forall j. \beta_j=\beta_{jpx}  \land \bigvee_{y\in Y} 
       		\Big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\Big)
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\Big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
       		\land \Big( 
       		\Pred_{OT_{pxy}}
       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\Big)
       		$

@@

      	\begin{small}     	
$\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{p\in P} (
	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
{~}\hspace{1cm}~ \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\Big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
\land \Pred_{OT_{pxy}}\\
~\hspace*{8.5em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\Big)
\\
{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\Big( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
\land \alpha\!=\!\alpha_{pxy} \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\Big)$
  \end{small}

@@

 Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
 $\Leaves(P)=p_l^{l\in L_P}$.
 Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
 $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
 We will consider the relation
%\footnote{$\uplus$ is defined on sets as the disjoint union 
% of the contained indexed 
% sets} 
$\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
 t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
   where $\mathcal{S}_P$ is the set of states of the open automaton of $P$.	We will prove 
 that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
 states: $(\ostate{s_{i}^{i \in L_P\uplus L}},\ostate{{t}_{i}^{i \in L'}\uplus 
 	{s}_{i}^{i \in L_P}}|\Pred_{s,t})\in\mathcal{R}'$. %Those are states of the open 
 %	automata of 
 %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
 Consider an 
 open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
 %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
 %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
 \\[-2ex]     
 \[P[Q]_{j_0}\models\openrule
 {
 	\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
 { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
 			L_P\uplus 
 			L}}}\]
 Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
 Lemma~\ref{lem-decompose} we have:\\[-2ex]
 	\begin{mathpar}
 P\models{\openrule
 	{
 		\beta_j^{j\in J'}, 
 		\Pred\,',  
 		\Post\,'}
 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {\alpha}
 		\ostate{s_{i}'^{\,i\in L_P}}}
 }\\
 Q\models{\openrule
 	{
 		\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 		\Post\,''}
 	{\ostate{s_{i}^{i\in L}} \OTarrow {\alpha_Q}
 		\ostate{s_{i}'^{\,i\in L}}}
 }\end{mathpar}
 and  $\Pred_{OT}\iff \Pred\,'
 \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
 \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
 		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
 $OT'_x$ 
 of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
 \begin{mathpar}
 Q'\models\openrule
 {
 	\beta_{j x}^{j\in J\cap\Holes(Q)}, 
 	\Pred_{OT_x},\Post_{OT_x}}
 {\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
 \end{mathpar}
 and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
 		L'}}|\Pred_{s x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred_{s,t} \land \Pred\,''
 \implies$\\ $\displaystyle{\bigvee_{x\in X}
 \Big( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
 \Pred_{OT_x}
 \land \alpha_Q\!=\!\alpha_x \land  
 \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)}$

@@

 \noindent                        
 \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
 \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
 	%reversed 
 	%substitution 
 	\implies  \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 	\Big( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 	\Pred_{OT_x}
 	\land \alpha_Q\!=\!\alpha_x \land  
 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)\land
 }
 \\~~\hspace*{3.5em}~\Pred\,'\land\alpha_Q=\beta_{j_0} \\
 	\implies
 	 \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 		\Big( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
 		\Pred\,'\land \Pred_{OT_x}
 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
 		~\hspace*{3.5em}~ \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)
 	 $\end{small}
